\documentclass[11pt]{article}

\title{CV}
\author{Jaime Rivera}

\begin{document}

\maketitle



\section{ \textit {Personal Information}}

\begin{itemize}
\item Name: Jaime Rivera
\item UC Merced email address: Jrivera73@ucmerced.edu
\end{itemize}


\section{\textit {Education}}

\begin{itemize}
  \item University of California, Merced: Anticipated Graduation Date: May 20, 2021  
  
  \item Major: Computer Science and Engineering, GPA: 3.304 
  
   \item Coursework: Data Structure, Object Orientated Programming, Java
   
    \item Technical Skills: C++, Java, Html and CSS, AutoCAD, and SolidWorks
    
     \item Organizations: Q – Project and American Institute of Aeronautics and Astronautics
  
\end{itemize}





\section{ \textit {Work Experience}}

\begin{itemize}

\item   {\textbf{Amigos Nursery}}: 

\begin{itemize}
\item  Los Angeles 2018: Team member in Landscaping/Construction: Worked with others in cleaning, planting, lifting, and delivering any kind of landscaping work to customers and other companies. 
 \end{itemize} 

 
\item  {\textbf{St. Lawrence Church}}: 

\begin{itemize}
\item Los Angeles 2016: Tutor Kids Grade Level 1st – 5th grade: My goal was to help kids be more proficient in their Math and English skills. 
 \end{itemize} 

 \end{itemize} 

\section{\textit {Projects}}

\begin{itemize}


\item Q – Project: 

    \begin{itemize}
     \item  Goal: “At the speed of technology” the goal for the Q – Project members is to gain skills necessary to be competitive job applicants.
     \end{itemize}
     
     \begin{itemize}
     \item  Contribution: Part of the Robot design team, our goal was to design a Prototype Mars Rover to showcase at the Barns ‘n Noble Fair in Merced
     \end{itemize} 
   
     
     
     
\item Rocket Project: 

     \begin{itemize}
     \item  Goal: To shape our aerospace professionalism by actively participating in the projects offered.
     \end{itemize} 
     
     \begin{itemize}
     \item Contribution: Design and build a “Level 1” rocket with my teammates, which can fly and meet certain requirements. 
     \end{itemize} 
     
     
     
\item Java 

     \begin{itemize}
     \item  Description: Designing projects using the language Java in Eclipse. Projects can be found in my GitHub Page. 
     \end{itemize} 
     
     \end{itemize} 



\section{\textit {Clubs}}

\begin{itemize}

\item Hermanos Unidos: Merced, Fall 2018    
\begin{itemize}
     \item  Hispanic driven club where “family” is key in building connections and relationships with other’s while volunteering in events and building a healthy bond with our hermanos. 
\end{itemize}   
                                                                             
\item Investment Club: Merced, Spring 2019
\begin{itemize}
     \item  Instructional knowledge in how to investment and examine the stock market. 
\end{itemize}    

\item Boxing Club: Merced, Fall 2017
\begin{itemize}
     \item Learning Self-defense while still maintaining a respectful relationship with your peers. 
\end{itemize}  
                                                                                             

\end{itemize}












\end{document}