\documentclass[11pt]{article}

\title{CSE - 015: Homework 2: Propositional Logic and Variables}
\author{Jaime Rivera}

\begin{document}
\maketitle

\section{Knowledge Representation:}

\begin{itemize}
\item It is not cloudy and it is not raining. 

\begin{itemize}
\item Solution: Let p = It is not cloudy, and let q = it is not raining, then $ -p \wedge -q$
 \end{itemize} 


\item I like to eat apples and bananas.

\begin{itemize}
\item Solution: Let p = I like to eat apples, and q = I like to eat bananas, then $p \wedge q$
 \end{itemize} 
 
\item Behind the clouds the sun is shining.

\begin{itemize}
\item Solution: Let p = Behind the clouds the sun is shinning, then  $ p  $
 \end{itemize} 
 
\item If a function is differentiable then the function is continuous. 

\begin{itemize}
\item Solution: Let p = If a function is differentiable, and q = the function is continuous, then $ p \to q $
 \end{itemize} 

 \item I will study for the final otherwise I will fail. 

\begin{itemize}
\item Solution: Let p =  I will study for the final, and q = I will fail, then $ p \to q $
 \end{itemize} 

\end{itemize}




\section{Equivalence in Propositional Logic:}


\begin{itemize}
\item 1. $p  \wedge  q$ and $p  \vee  \neg q$ 

\begin{itemize}
\item Solution: They are not equivalent, because  For p = T and q = F, $T  \wedge F$ = F and $T \vee \neg F $ = T, which makes them not equivalent.

\begin{tabular}{|c|c|c|c|}
\hline
$p$ & $q$ & $p \land q$ & $p \lor  \lnot q$ \\
\hline
0 & 0 & 0 & 1 \\
0 & 1 & 0 & 0 \\
1 & 0 & 0 & 1 \\
1 & 1 & 1 & 1 \\
\hline
\end{tabular}

 \end{itemize} 

\item 2. $p \vee q$ and  $\neg p \vee  \neg q $

\begin{itemize}
\item Solution: They are not equivalent, because for p = F and q = F, $F \vee F$ = F and $\neg F \vee \neg F $= T, which makes them not equivalent.

\begin{tabular}{|c|c|c|c|}
\hline
$p$ & $q$ & $p \lor q$ & $ \lnot p \lor  \lnot q$ \\
\hline
0 & 0 & 0 & 1 \\
0 & 1 & 1 & 1 \\
1 & 0 & 1 & 1 \\
1 & 1 & 1 & 0 \\
\hline
\end{tabular}

 \end{itemize} 

\item 3. $p \to q$ and $ \neg q \to \neg p $

\begin{itemize}
\item Solution: They are equivalent. Proof: Contra Positive, TruthTable rows Match.

\begin{tabular}{|c|c|c|c|}
\hline
$p$ & $q$ & $p \to q$ & $ \lnot q \to  \lnot p$ \\
\hline
0 & 0 & 1 & 1 \\
0 & 1 & 1 & 1 \\
1 & 0 & 0 & 0 \\
1 & 1 & 1 & 1 \\
\hline
\end{tabular}

 \end{itemize} 
 
\item 4. $p \to q $ and $ \neg p \vee q $

\begin{itemize}
\item Solution: They are equivalent. Proof The TruthTable, the rows match.

\begin{tabular}{|c|c|c|c|}
\hline
$p$ & $q$ & $p \to q$ & $ \lnot p \lor q$ \\
\hline
0 & 0 & 1 & 1 \\
0 & 1 & 1 & 1 \\
1 & 0 & 0 & 0 \\
1 & 1 & 1 & 1 \\
\hline
\end{tabular}

 \end{itemize} 
 
\item 5. $ \neg (p \wedge q) $ and $ \neg p \vee  \neg q $

\begin{itemize}
\item Solution: They are equivalent. Proof: De Morgan's Law, TruthTable rows Match 

\begin{tabular}{|c|c|c|c|}
\hline
$p$ & $q$ & $ \lnot (p \land q)$ & $ \lnot p \lor  \lnot q$ \\
\hline
0 & 0 & 1 & 1 \\
0 & 1 & 1 & 1 \\
1 & 0 & 1 & 1 \\
1 & 1 & 0 & 0 \\
\hline
\end{tabular}

 \end{itemize} 
 
\end{itemize}


\end{document}